The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-02-20 paper/draft.tex
add some refs to commented text

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
%% Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact that some lineages radiate explosively following
%% island colonisation, while others remain one single species (Price/Chase) (eg. \cite{price2004speciation}).

%% Also: Ecological Opportunity and Adaptive Radiation, Stroud \& Losos 2016: ``Does the concept have predictive value[...]?'' \cite{stroud2016ecological}
%% Phylogenetic niche conservatism, phylogenetic signal and the relationship between phylogenetic relatedness and ecological similarity among species, Losos 2008: ecological vs. phylogenetic similarity \cite{losos2008phylogenetic}
Still, the proposed mechanisms so far include only ecological or geo-morphological processes,
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via \& West 2008, Via 2001 and references therein).

>>>>

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
%% Yet, there are numerous examples for fascinating patterns of trait distributions and evolution on islands, such as island syndromes[, ...] or the fact of explosively radiating lineages (Hughes \& Eastwood 2006, Kocher 2004)
%%, while others remain one single species (Price/Chase) (eg. \cite{price2004speciation}).

%% Also: Ecological Opportunity and Adaptive Radiation, Stroud \& Losos 2016: ``Does the concept have predictive value[...]?'' \cite{stroud2016ecological}
%% Phylogenetic niche conservatism, phylogenetic signal and the relationship between phylogenetic relatedness and ecological similarity among species, Losos 2008: ecological vs. phylogenetic similarity \cite{losos2008phylogenetic}
Still, the proposed mechanisms so far include only ecological or geo-morphological processes (Rundell \& Price 2009, Esselstyn et al. 2011),
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via \& West 2008, Via 2001 and references therein).
